### 2021-12-08 text/outline/draft.tex
update gasp optimal bdy; setup thresholding method

To our knowledge this is the first paper to examine single-cell CRISPR screens from a rigorous statistical perspective. We hope that this work can serve as an introduction to the broader statistics community to an emerging class functional genomics assays that likely will exert a major impact on biology research in the coming years \cite{Przybyla2021}. Additionally, this is the first work to leverage the ondisc-Nextflow-cloud/HPC technology stack, an (in our view) tightly-integrated, user-friendly, and powerful set of computational tools for out-of-memory and massively distributed single-cell analysis.

>>>>

To our knowledge this is the first paper to examine single-cell CRISPR screens from a rigorous statistical perspective. We hope that this work can help introduce the broader statistics community to an emerging class functional genomics assays that likely will exert a major impact on biology research in the coming years \cite{Przybyla2021}. Additionally, this is the first work to leverage the ondisc-Nextflow-cloud/HPC technology stack, an (in our view) tightly-integrated, user-friendly, and powerful set of computational tools for out-of-memory and massively distributed single-cell analysis.
